Characteristics of Top Songs Has Changed from Pandemic Brain

### 2024-04-14 paper/paper.qmd
Updated formatting of paper and added more graphs for the model

library(tidyverse)
library(arrow)
library(ggcorrplot)
library(ggplot2)
library(knitr)
library(modelsummary)

@@

playlist_analysis_data |> 
  head() |>
  kable()
```

@@

### Scale and Modality
```{r}
#| label: fig-key-mode-bar
#| fig-cap: Proportion of songs in different scales before 2020 versus during and after 2020
#| echo: false
#| warning: false
#| message: false

@@

proportion_of_each_mode |> 
  ggplot(mapping = aes(x = mode_name, y = proportion_mode_name)) +
  facet_wrap(facets = vars(period), dir = "v") + 
  geom_bar(stat = "identity", binwidth = 3) +
  theme_minimal() +
  labs(x = "Modality",
       y = "Proportion") + 
  theme(axis.text.x = element_text(angle = 90))
```
```{r}
#| label: tbl-mode-table
#| tbl-cap: Proportion of songs whose modality is in a major or minor key before 2020 versus during and after 2020
#| echo: false
#| warning: false
#| message: false

@@

playlist_analysis_data |> 
  # Filter for "Before Pandemic"
  filter(period == "Before Pandemic") |>
  # Choose track_duration_ms
  select(track_duration_ms) |>
  # Rename columns
  rename (
    "Duration of song (in ms)"= track_duration_ms
  ) |>
  summary() |>
  kable()
```
```{r}
#| label: tbl-track-duration-stats-during-after
#| tbl-cap: Minimum, quartiles, median, and maximum of track duration (in ms) during and after 2020
#| echo: false
#| warning: false
#| message: false

@@

playlist_analysis_data |> 
  # Filter for "During and After Pandemic"
  filter(period == "During and After Pandemic") |>
  # Choose loudness
  select(loudness) |>
  # Rename columns
  rename (
    "Loudness of song (in dB)"= loudness
  ) |>
  summary() |>
  kable()
```

@@

modelplot(hit_song_model_results, conf_level = 0.9) +
  labs(x = "90 per cent credibility interval")
```

@@

## Model details {#sec-model-details}
[To Do]

### Posterior predictive check

### Diagnostics

@@

>>>>

library(tidyverse)
library(arrow)
library(ggcorrplot)
library(ggplot2)
library(knitr)
library(modelsummary)
library(rstanarm)

@@

playlist_analysis_data |> 
  select(hit_year, track_duration_ms, tempo, loudness, mode_name, key_mode, period) |>
  head() |>
  kable()
```
Not seen in @tbl-dataset-preview, before_pandemic, major, and minor are numerical versions of the mode_name and period columns.

@@

### Scale and Modality

proportion_of_each_mode |> 
  ggplot(mapping = aes(x = mode_name, y = proportion_mode_name)) +
  facet_wrap(facets = vars(period), dir = "v") + 
  geom_bar(stat = "identity", binwidth = 3) +
  theme_minimal() +
  labs(x = "Modality",
       y = "Proportion") + 
  theme(axis.text.x = element_text(angle = 90))
```

```{r}
#| label: tbl-mode-table
#| tbl-cap: Proportion of songs whose modality is in a major or minor key before 2020 versus during and after 2020
#| echo: false
#| warning: false
#| message: false

```{r}
#| label: fig-key-mode-bar
#| fig-cap: Proportion of songs in different scales before 2020 versus during and after 2020
#| echo: false
#| warning: false
#| message: false

@@

@@

playlist_analysis_data |> 
  # Filter for "Before Pandemic"
  filter(period == "Before Pandemic") |>
  # Choose track_duration_ms
  select(track_duration_ms) |>
  # Rename columns
  rename (
    "Duration of song (in ms)"= track_duration_ms
  ) |>
  summary() |>
  kable()
```

```{r}
#| label: tbl-track-duration-stats-during-after
#| tbl-cap: Minimum, quartiles, median, and maximum of track duration (in ms) during and after 2020
#| echo: false
#| warning: false
#| message: false

@@

playlist_analysis_data |> 
  # Filter for "During and After Pandemic"
  filter(period == "During and After Pandemic") |>
  # Choose loudness
  select(loudness) |>
  # Rename columns
  rename (
    "Loudness of song (in dB)"= loudness
  ) |>
  summary() |>
  kable()
```
\newpage

@@

modelplot(hit_song_model_results, conf_level = 0.9) +
  labs(x = "90 per cent credibility interval")
```
\newpage

@@

@@

## Posterior predictive check for model {#sec-model-details-posterior-check}
```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-posteriorpredictive
#| fig-cap: "How the data impacts how the model fits"
#| fig-subcap: ["Posterior prediction check for the model"]
#| layout-ncol: 1

rstanarm::pp_check(hit_song_model_results) +
  theme_classic() +
  theme(legend.position = "bottom")
```
\newpage

## Diagnostics for model {#sec-model-details-diagnostics}
```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-convergencecheck
#| fig-cap: "Checking the convergence of the MCMC algorithm for hit song model"
#| fig-subcap: ["Trace plot for model", "Rhat plot for model"]
#| layout-ncol: 2

plot(hit_song_model_results, "trace")

plot(hit_song_model_results, "rhat") + theme_minimal()
```
